Case Study: 16S microbiome data (Goodrich et al., 2014)

### 2018-07-11 datasets/microbiome/microbiome-goodrich.Rmd
Add uninf covariate for goodrich

Here we download and analyze the Goodrich obesity (OB) dataset
[(Goodrich et al., 2014)](https://doi.org/10.1016/j.cell.2014.09.053).
The dataset includes fecal samples from 428 individuals with lean body mass index (BMI < 25),
and 185 obese individuals (BMI > 30). We'll download the processed OTU tables from
Zenodo and unzip them in the `benchmark-fdr/datasets/microbiome/data` folder.

We expect few or no truly differentially abundant OTUs ([Finucane et al., 2014](https://doi.org/10.1371/journal.pone.0084689) and [Walters et al., 2014](https://doi.org/10.1016%2Fj.febslet.2014.09.039)), so this study provides a real-life "null" example.

>>>>

Here we download and analyze the Goodrich obesity (OB) dataset
[(Goodrich et al., 2014)](http://dx.doi.org/10.1016/j.cell.2014.09.053).
The dataset includes fecal samples from 428 individuals with lean body mass index (BMI < 25),
and 185 obese individuals (BMI > 30). We'll download the processed OTU tables from
Zenodo and unzip them in the `benchmark-fdr/datasets/microbiome/data` folder.

We expect few or no truly differentially abundant OTUs ([Finucane et al., 2014](http://dx.doi.org/10.1371/journal.pone.0084689) and [Walters et al., 2014](https://dx.doi.org/10.1016%2Fj.febslet.2014.09.039)), so this study provides a real-life "null" example.
